SPARQL on the open, decentralised Web

### 2016-06-01 dissertation/related.tex
link my own to ldf

Verborgh et al. \cite{ldf1} wanted a system that would be able to
answer individual triple patterns to enable clients to answer queries,
and to do so, they employed hypermedia, and formulated this as Triple
Pattern Fragments. The key to this hypermedia is that an answer does
not only include the data, but also metadata, importantly a
cardinality estimate for the triple pattern, and also control
information, that tells a client explicitly in every response how
further interaction should be done, like obtaining further data.

>>>>

An example of this use is the work considered in
Section~\ref{sec:conlapis}, another example is the new direction
proposed by Verborgh et al. \cite{ldf1} who wanted a system that would
be able to answer individual triple patterns to enable clients to
answer queries, and to do so, they employed hypermedia, and formulated
this as Triple Pattern Fragments. The key to this hypermedia is that
an answer does not only include the data, but also metadata,
importantly a cardinality estimate for the triple pattern, and also
control information, that tells a client explicitly in every response
how further interaction should be done, like obtaining further data.
